\theseminartitle \\ \small \thetitle

### 2021-09-15 tex/paper.tex
Added further explanation for evaluation of benchmarks

\loadglsentries{glossary}
%*********************************************************************%
% META                                                                %
%*********************************************************************%
\newcommand{\university}{Saarland University}
\newcommand{\school}{Saarland Informatics Campus}
\newcommand{\thetitle}{Seminar: Systems Benchmarking}
\newcommand{\shorttitle}{Seminar: Systems Benchmarking}
\newcommand{\thedate}{April 15}
\newcommand{\thegermandate}{15. April}

@@

\paragraph{Relevance} TODO: Short explanation
\paragraph{Reproducibility} TODO: Short explanation
\paragraph{Fairness} TODO: Short explanation
\paragraph{Verifiability} TODO: Short explanation
\paragraph{Usability} TODO: Short explanation

@@

\section{Continuous Benchmarking}
\subsection{Definition}
\subsection{Usages}
\subsection{Challenges}

>>>>

\loadglsentries{glossary}
%*********************************************************************%
% META                                                                %
%*********************************************************************%
\newcommand{\university}{Saarland University}
\newcommand{\school}{Saarland Informatics Campus}
\newcommand{\thetitle}{Seminar: Systems Benchmarking}
\newcommand{\shorttitle}{Seminar: Systems Benchmarking}
\newcommand{\thedate}{\today{}}
\newcommand{\thegermandate}{15. April}

@@

\paragraph{Relevance} For a benchmark to be meaningful it is important that it, at least to a certain extent, reproduces some scenarios with real world application. This is what the "Relevance" of a benchmark refers to. It tries to define how relevant the produced information is to a potential user of a software. According to Kistowski et al. this makes it "perhaps the most important characteristic" (\cite{kistowski2015} p. 334). However the relevance of a benchmark may also limits the benchmarks applicability meaning, that a highly relevant benchmark for a specific system or component might only narrow applicability while benchmarks with a broad applicability will have a lower relevance but for a wider selection of applications. Kitowski et al. further elaborate on this with specific examples (\cite{kitowski2015} p. 334f)

\paragraph{Reproducibility} Reproducability ensures that it is possible for a third party to produce ideally the same results for a given test environment. Reproducability covers both the consistency between mutliple runs on the same system as well as creating the same results on another environment with a semantically equivalent configuration.

However, with modern hard- and software systems, optimal reproducability has become challenging. For both hard- and software there are several factors that induce variability. From a hardware side things such as the physical disc layout or network connections may affect benchmarking results. For software systems the causes for variability stem from various different sources. from a low-level perspective, things such as thread scheduling can influence the benchmark results. From a higher level perspective a benchmark has to consider the configurability of a software system itself. Modern software systems often offer lots of different configuration options which can be used to create a tailor made system-variant. En- or disabling a specific feature might heavily influence the performance of a benchmark.

According to Huppler, an ideal benchmark result should be definable as a function fo a hard- and software configuration (See \cite{huppler2009} p. 335). However for real-world applications, modelling such a function is far too complex which requires the benchmark designer to try to model reproducability in other ways. In the end the reproducability of a benchmark is heavuly dependent on the ability to reproduce the benchamrking environment that was used to create this specific benchmark.

\paragraph{Fairness} TODO: Short explanation
\paragraph{Verifiability} TODO: Short explanation
\paragraph{Usability} TODO: Short explanation

@@

\section{Continuous Benchmarking}
\subsection{Definition}
\subsection{Strategies and Opportunities}
\subsection{Challenges}
